Methods

### 2024-01-27 methods.qmd
Cleaned up code added comments
Adding over 45 flag, more clustering, impute chd prev

@@

@@

@@

>>>>

nearest neighbours to impute chd prevalence

@@

Imputing data in Census 2021:

<https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/methodologies/itemeditingandimputationprocessforcensus2021englandandwales>

@@

Used October 2022 gp list size by age and gender to calculate % of list size aged 45+

@@

<https://www.statology.org/k-medoids-in-r/>

https://www.rdocumentation.org/packages/cluster/versions/2.1.6

look at 18:50 in this video: https://www.youtube.com/watch?v=dKXTNxNDpMA

## Mapping new GP practices to old

### To obtain CHD prevalence for as many new practices as possible

link to to the blog

<https://the-strategy-unit.github.io/data_science/blogs/posts/2024-01-17_nearest_neighbour.html>

151 missing and this finds all but 26 using a 1.5km radius - more or less?
